---
title: "About me"
description: |
 My career and interests
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

I graduated from the University of Las Palmas de Gran Canaria (2014) with a B.S. in Marine Science. Delving into the scientific knowledge associated with my undergraduate studies pushed me to develop a great interest in ocean exploration, allowing me to pursue a career in field research. At the Spanish Bank of Algae, I performed bioprospecting tasks in the Canary Islands, Algeria, and Israel. In addition, professional diving training and extensive previous experiences allowed me to participate in environmental projects for private and government-owned companies in Spain. I specialized in campaign logistics, scientific diving techniques, oceanographic monitoring, and motorboat and ROV operations. Currently, I am studying a master's at the University of California Santa Barbara, focusing on marine resources management. My passion for ocean-related issues transcends my professional life. I am an enthusiast free diver and surfer who also has sailed across the Atlantic.

<br>

<head>

<link type="text/css" rel="stylesheet" href="https://cdnjs.cloudflare.com/ajax/libs/lightgallery/1.6.0/css/lightgallery.min.css" />
<script src="https://cdnjs.cloudflare.com/ajax/libs/lightgallery-js/1.4.1-beta.0/js/lightgallery.min.js"></script>

<!-- lightgallery plugins -->
<script src="https://cdnjs.cloudflare.com/ajax/libs/lg-fullscreen/1.2.1/lg-fullscreen.min.js"></script>
<script src="https://cdnjs.cloudflare.com/ajax/libs/lg-thumbnail/1.2.1/lg-thumbnail.min.js"></script>

</head>

```{css}
#lightgallery > a > img:hover {
   transform: scale(1.15, 1.15);
   transition: 0.4s ease-in-out;
   cursor: pointer;
}
```

```{r include = FALSE}
# Load the functions we have created
source(here::here("R/functions.R"))
```

```{r,out.width='50%',fig.show='hold'}
# Create layout
withTags(
  div(
    class = "row",
    id = "lightgallery",
    tagList(
      make_gallery_layout()
    )
  )
)

```

<script type="text/javascript">
    lightGallery(document.getElementById('lightgallery'));
</script>


